### 2020-09-17 submission/manuscript.Rmd
Add Table 1 and move packages to YAML

---
bibliography: references.bib
output:
  pdf_document:
    keep_tex: true
    includes:
      in_header: header.tex
csl: mbio.csl
geometry: margin=1.0in
---

@@

library(tidyverse)
library(knitr)
suppressPackageStartupMessages(library(here))

@@

@@

**Figure 2.**

>>>>

---
bibliography: references.bib
output:
  pdf_document:
    keep_tex: true
header-includes:
 - \usepackage{booktabs}
 - \usepackage{longtable}
 - \usepackage{array}
 - \usepackage{multirow}
 - \usepackage{wrapfig}
 - \usepackage{float}
 - \usepackage{colortbl}
 - \usepackage{pdflscape}
 - \usepackage{tabu}
 - \usepackage{threeparttable}
 - \usepackage{threeparttablex}
 - \usepackage[normalem]{ulem}
 - \usepackage{makecell}
 - \usepackage{setspace}
 - \doublespacing
 - \usepackage[left]{lineno}
 - \linenumbers
 - \modulolinenumbers
 - \usepackage{helvet} % Helvetica font
 - \renewcommand*\familydefault{\sfdefault} % Use the sans serif version of the font
 - \usepackage[T1]{fontenc}
csl: mbio.csl
geometry: margin=1.0in
---

@@

library(tidyverse)
library(glue)
library(kableExtra)
library(knitr)
suppressPackageStartupMessages(library(here))

@@

**Table 1. Summary of studies used in the analysis.** For all studies, the number of sequences used from each study was rarefied to the smallest sample size. A graphical represenation of the distribution of sample sizes for each study and the samples that were removed from each study are provided in Figure S1.

```{r}
read_tsv(here('data/process/study_summary_statistics.tsv')) %>%
  arrange(nice_name) %>%
  mutate(name_ref = glue("{nice_name} ({reference})"),
    total_seqs=format(total_seqs, big.mark=",", trim=TRUE),
    median=format(as.integer(median), big.mark=",", trim=TRUE),
    min=format(min, big.mark=",", trim=TRUE),
    max=format(max, big.mark=",", trim=TRUE),
    range = glue("{min}-{max}"),
    n_samples = n_samples,
    fold_difference = round(fold_difference, 1)) %>%
  select(name_ref, n_samples, total_seqs, median, range, fold_difference) %>%
  kable("latex", booktabs=TRUE, escape=F, align="lrrrrr", linesep="",
		col.names = linebreak(c("Study (Ref)", "Samples", "Total\nsequences", "Median\nsequences",
			"Range of\nsequences", "Fold-difference\nbetween largest\nand smallest sample"), align="c")
	) %>%
	row_spec(0, bold=T)
```

@@

**Figure 2.**
v

### 2020-09-17 submission/manuscript.tex
Add Table 1 and move packages to YAML

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1.0in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\providecommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}

  \title{}
    \pretitle{\vspace{\droptitle}}
  \posttitle{}
    \author{}
    \preauthor{}\postauthor{}
    \date{}
    \predate{}\postdate{}

\usepackage{helvet} % Helvetica font
\renewcommand*\familydefault{\sfdefault} % Use the sans serif version of the font
\usepackage[T1]{fontenc}

\usepackage[none]{hyphenat}

\usepackage{setspace}
\doublespacing
\setlength{\parskip}{1em}

\usepackage{lineno}

\usepackage{pdfpages}

@@

@@

\textbf{Figure 2.}

>>>>

\documentclass[]{article}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\usepackage[margin=1.0in]{geometry}
\usepackage{graphicx}
% Redefine \includegraphics so that, unless explicit options are
% given, the image width will not exceed the width of the page.
% Images get their normal width if they fit onto the page, but
% are scaled down if they would overflow the margins.
\makeatletter
\def\ScaleIfNeeded{%
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother
\let\Oldincludegraphics\includegraphics
{%
 \catcode`\@=11\relax%
 \gdef\includegraphics{\@ifnextchar[{\Oldincludegraphics}{\Oldincludegraphics[width=\ScaleIfNeeded]}}%
}%
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}

\author{}
\date{\vspace{-2.5em}}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{setspace}
\doublespacing
\usepackage[left]{lineno}
\linenumbers
\modulolinenumbers
\usepackage{helvet} % Helvetica font
\renewcommand*\familydefault{\sfdefault} % Use the sans serif version of the font
\usepackage[T1]{fontenc}

@@

\textbf{Table 1. Summary of studies used in the analysis.} For all
studies, the number of sequences used from each study was rarefied to
the smallest sample size. A graphical represenation of the distribution
of sample sizes for each study and the samples that were removed from
each study are provided in Figure S1.

\begin{tabular}{lrrrrr}
\toprule
\textbf{Study (Ref)} & \textbf{Samples} & \textbf{\makecell[c]{Total\\sequences}} & \textbf{\makecell[c]{Median\\sequences}} & \textbf{\makecell[c]{Range of\\sequences}} & \textbf{\makecell[c]{Fold-difference\\between largest\\and smallest sample}}\\
\midrule
Bioethanol (NA) & 95 & 3,972,943 & 16,015 & 3,688-356,136 & 96.6\\
Human (NA) & 490 & 20,909,768 & 32,505 & 10,523-430,415 & 40.9\\
Lake (NA) & 52 & 3,169,868 & 69,041 & 15,347-112,871 & 7.4\\
Marine (NA) & 7 & 1,391,396 & 193,464 & 133,516-254,060 & 1.9\\
Mice (NA) & 348 & 2,813,747 & 6,477 & 1,804-30,565 & 16.9\\
Peromyscus (NA) & 111 & 1,555,545 & 12,446 & 4,464-33,644 & 7.5\\
Rainforest (NA) & 69 & 946,295 & 11,561 & 4,932-37,767 & 7.7\\
Rice (NA) & 490 & 22,591,168 & 43,216 & 2,776-193,464 & 69.7\\
Seagrass (NA) & 286 & 4,130,454 & 13,567 & 1,803-45,191 & 25.1\\
Sediment (NA) & 58 & 1,154,174 & 17,584 & 7,685-68,321 & 8.9\\
Soil (NA) & 18 & 956,656 & 51,844 & 47,806-59,956 & 1.3\\
Stream (NA) & 201 & 21,162,574 & 90,159 & 9,175-390,964 & 42.6\\
\bottomrule
\end{tabular}

@@

\textbf{Figure 2.} v
